---
title: "Node Modification"
author: "Jim Hester"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Node Modification}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Modifying Existing XML

Modifying existing XML can be done in xml2 by using the replacement functions
of the accessors. They all have methods for both individual `xml_node` objects
as well as `xml_nodeset` objects. If a vector of values is provided it is
applied piecewise over the nodeset, otherwise the value is recycled.

## Text Modification ##

Text modification only happens on text nodes. If a given node has more than one
text node only the first will be affected. If you want to modify additional
text nodes you need to select them explicitly with `/text()`.

```{r}
library(xml2)
x <- read_xml("<p>This is some <b>text</b>. This is more.</p>")
xml_text(x)

xml_text(x) <- "This is some other text."
xml_text(x)

# You can avoid this by explicitly selecting the text node.
x <- read_xml("<p>This is some text. This is <b>bold!</b></p>")
text_only <- xml_find_all(x, "//text()")

xml_text(text_only) <- c("This is some other text. ", "Still bold!")
xml_text(x)
xml_structure(x)
```

## Attribute Modification ##

Attributes are modified one at a time with `xml_attr()` or all at once with
`xml_attrs()`. In both cases using `NULL` as the value will remove the
attribute completely.

```{r}
x <- read_xml("<a href='invalid!'>xml2</a>")
xml_attr(x, "href")

xml_attr(x, "href") <- "https://github.com/hadley/xml2"
xml_attr(x, "href")

xml_attrs(x) <- c(id = "xml2", href = "https://github.com/hadley/xml2")
xml_attrs(x)
cat(as.character(x))

xml_attrs(x) <- NULL
cat(as.character(x))
```

## Name Modification ##

Node names are modified with `xml_name()`.

```{r}
x <- read_xml("<a><b/></a>")
x
xml_name(x)
xml_name(x) <- "c"
x
```

# Node modification #
All of these functions have a `copy` argument. If this is set to `FALSE` they
will remove the new node from its location before inserting it into the new
location. Otherwise they make a copy of the node before insertion.

## Replacing existing nodes ##
```{r}
x <- read_xml("<parent><child>1</child><child>2<child>3</child></child></parent>")
children <- xml_children(x)
t1 <- children[[1]]
t2 <- children[[2]]
t3 <- xml_children(children[[2]])[[1]]

xml_replace(t1, t3)
x
```

## Append sibling ##
```{r}
x <- read_xml("<parent><child>1</child><child>2<child>3</child></child></parent>")
children <- xml_children(x)
t1 <- children[[1]]
t2 <- children[[2]]
t3 <- xml_children(children[[2]])[[1]]

xml_add_sibling(t1, t3)
x

xml_add_sibling(t3, t1, where = "before")
x
```

## Add a child ##
```{r}
x <- read_xml("<parent><child>1</child><child>2<child>3</child></child></parent>")
children <- xml_children(x)
t1 <- children[[1]]
t2 <- children[[2]]
t3 <- xml_children(children[[2]])[[1]]

xml_add_child(t1, t3)
x

xml_add_child(t1, read_xml("<test/>"))
x
```

## Namespaces ##

We want to construct a document with the following namespace layout. (From
http://stackoverflow.com/questions/32939229/creating-xml-in-r-with-namespaces/32941524#32941524).
```xml
<?xml version = "1.0" encoding="UTF-8"?>
<sld xmlns="http://www.o.net/sld"
     xmlns:ogc="http://www.o.net/ogc"
     xmlns:se="http://www.o.net/se"
     version="1.1.0" >
<layer>
<se:Name>My Layer</se:Name>
</layer>
</sld>
```

```{r}
library(magrittr)
d <- xml_new_document() %>%
  xml_add_child("sld",
    xmlns = "http://www.o.net/sld",
    "xmlns:ogc" = "http://www.o.net/ogc",
    "xmlns:se" = "http://www.o.net/se",
    version = "1.1.0") %>%
  xml_add_child("layer") %>%
  xml_add_child("se:Name") %>%
  xml_root()

cat(as.character(d))
```
